---
title: "CPD-Seq Binned Graph Generation"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, //wsl.localhost/Ubuntu/home/ben/bioinformatics]
---

```{r setup_chunk}
library(knitr)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

rep = "rep2"
bioinformaticsDirectory = "//wsl.localhost/Ubuntu/home/ben/bioinformatics"

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0("Drosophila_CPDseq_chromatin_domains_analysis_output_",rep,.Platform$file.sep))
```

Get the relevant functions and binned counts data tables for graphing binned data
```{r prep_bin_data, message=FALSE}
source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "GraphBinnedData.R"))

# Get file paths related to genome-wide bin colors.
drosophilaChromatinDomainsDir = file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "data",
                                          "chromatin_domains", "drosophila")
binnedColorDomains100.000bpFilePath = file.path(drosophilaChromatinDomainsDir, 
                                                "drosophila_chromatin_color_domains_100000bp_binned.tsv")

# Get file paths related to CPD data in genome-wide bins.
drosophilaDataDir = file.path(bioinformaticsDirectory, "data", "sequencing_data", "Marian", "Drosophila_CPDseq")
noUV100.000bpFilePath = file.path(drosophilaDataDir, paste0("Dm_no_UV_",rep),
                                  paste0("Dm_no_UV_",rep,"_singlenuc_context_mutations_100000bp_binned.tsv"))
uva100.000bpFilePaths = list(
  min0  = file.path(drosophilaDataDir, paste0("Dm_UVA_0min_",rep), paste0("Dm_UVA_0min_",rep,"_singlenuc_context_mutations_100000bp_binned.tsv")),
  min10 = file.path(drosophilaDataDir, paste0("Dm_UVA_10min_",rep), paste0("Dm_UVA_10min_",rep,"_singlenuc_context_mutations_100000bp_binned.tsv")),
  min20 = file.path(drosophilaDataDir, paste0("Dm_UVA_20min_",rep), paste0("Dm_UVA_20min_",rep,"_singlenuc_context_mutations_100000bp_binned.tsv")),
  min30 = file.path(drosophilaDataDir, paste0("Dm_UVA_30min_",rep), paste0("Dm_UVA_30min_",rep,"_singlenuc_context_mutations_100000bp_binned.tsv"))
)
noUVA30min100.000bpFilePath = file.path(drosophilaDataDir, "Dm_no_UVA_30min_rep1", "Dm_no_UVA_30min_rep1_singlenuc_context_mutations_100000bp_binned.tsv")

# Get file paths for 10,000 bp genome-wide bins using the file paths for 100,000 bp bins.
binnedColorDomains10.000bpFilePath = sub("100000", "10000", binnedColorDomains100.000bpFilePath)
noUV10.000bpFilePath = sub("100000", "10000", noUV100.000bpFilePath)
uva10.000bpFilePaths = sapply(uva100.000bpFilePaths, function(x) sub("100000", "10000", x), simplify = FALSE)
noUVA30min10.000bpFilePath = sub("100000", "10000", noUVA30min100.000bpFilePath)

noUV10.000bpGenicFilePath = sub("mutations", "mutations_genic", noUV10.000bpFilePath)
uva10.000bpGenicFilePaths = sapply(uva10.000bpFilePaths, function(x) sub("mutations", "mutations_genic", x), simplify = FALSE)
noUVA30min10.000bpGenicFilePath = sub("mutations", "mutations_genic", noUVA30min10.000bpFilePath)

noUV10.000bpIntergenicFilePath = sub("genic", "intergenic", noUV10.000bpGenicFilePath)
uva10.000bpIntergenicFilePaths = sapply(uva10.000bpGenicFilePaths, function(x) sub("genic", "intergenic", x), simplify = FALSE)
noUVA30min10.000bpIntergenicFilePath = sub("genic", "intergenic", noUVA30min10.000bpGenicFilePath)

# Get scaling factors for the UVA data
uvaScalingFactors = list(
  min0 = 1.0,
  min10 = 1.0-0.531,
  min20 = 1.0-0.687,
  min30 = 1.0-0.792
)

noUVAScalingFactor = 1.0-0.1

# Parse the genome-wide bin files into counts tables.
noUV100.000bp = parseBinData(noUV100.000bpFilePath, binnedColorDomains100.000bpFilePath)
uva100.000bp = mapply(
  parseBinData, uva100.000bpFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE,
  MoreArgs = list(
    binnedColorDomainsFilePath = binnedColorDomains100.000bpFilePath,
    backgroundBinCountsFilePath = uva100.000bpFilePaths$min0
  )
)
noUVA30min100.000bp = parseBinData(noUVA30min100.000bpFilePath, binnedColorDomains100.000bpFilePath, scalingFactor = noUVAScalingFactor)

noUV10.000bp = parseBinData(noUV10.000bpFilePath, binnedColorDomains10.000bpFilePath)
uva10.000bp = mapply(
  parseBinData, uva10.000bpFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE,
  MoreArgs = list(
    binnedColorDomainsFilePath = binnedColorDomains10.000bpFilePath,
    backgroundBinCountsFilePath = uva10.000bpFilePaths$min0
  )
)
noUVA30min10.000bp = parseBinData(noUVA30min10.000bpFilePath, binnedColorDomains10.000bpFilePath, scalingFactor = noUVAScalingFactor)

noUV10.000bpGenic = parseBinData(noUV10.000bpGenicFilePath, binnedColorDomains10.000bpFilePath)
noUV10.000bpGenic[,Genic_Or_Intergenic := "Genic"]
uva10.000bpGenic = mapply(
  parseBinData, uva10.000bpGenicFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE,
  MoreArgs = list(
    binnedColorDomainsFilePath = binnedColorDomains10.000bpFilePath,
    backgroundBinCountsFilePath = uva10.000bpGenicFilePaths$min0
  )
)
captureOutput = lapply(uva10.000bpGenic, 
                       function(x) x[,Genic_Or_Intergenic := "Genic"])
noUVA30min10.000bpGenic = parseBinData(
  noUVA30min10.000bpGenicFilePath, binnedColorDomains10.000bpFilePath, scalingFactor = noUVAScalingFactor
)
noUVA30min10.000bpGenic[,Genic_Or_Intergenic := "Genic"]

noUV10.000bpIntergenic = parseBinData(noUV10.000bpIntergenicFilePath, binnedColorDomains10.000bpFilePath)
noUV10.000bpIntergenic[,Genic_Or_Intergenic := "Intergenic"]
uva10.000bpIntergenic = mapply(
  parseBinData, uva10.000bpIntergenicFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE,
  MoreArgs = list(
    binnedColorDomainsFilePath = binnedColorDomains10.000bpFilePath,
    backgroundBinCountsFilePath = uva10.000bpIntergenicFilePaths$min0
  )
)
captureOutput = lapply(uva10.000bpIntergenic, 
                       function(x) x[,Genic_Or_Intergenic := "Intergenic"])
noUVA30min10.000bpIntergenic = parseBinData(
  noUVA30min10.000bpIntergenicFilePath, binnedColorDomains10.000bpFilePath, scalingFactor = noUVAScalingFactor
)
noUVA30min10.000bpIntergenic[,Genic_Or_Intergenic := "Intergenic"]


# Combine the genic and intergenic data.
noUV10.000bpGenicVsIntergenic = rbindlist(list(noUV10.000bpGenic, noUV10.000bpIntergenic))
uva10.000bpGenicVsIntergenic = mapply(
  function(x,y) rbindlist(list(x,y)), 
  uva10.000bpGenic, uva10.000bpIntergenic,
  SIMPLIFY = FALSE
)
noUVA30min10.000bpGenicVsIntergenic = rbindlist(list(noUVA30min10.000bpGenic, noUVA30min10.000bpIntergenic))


# Get file paths for the gene bins data
noUVGeneBinFlankedFilePath = file.path(
  drosophilaDataDir, paste0("Dm_no_UV_",rep),
  paste0("Dm_no_UV_",rep,"_singlenuc_context_mutations_gene_bins_flanked.tsv")
)
uvaGeneBinFlankedFilePaths = list(
  min0  = file.path(drosophilaDataDir, paste0("Dm_UVA_0min_",rep),
                    paste0("Dm_UVA_0min_",rep,"_singlenuc_context_mutations_gene_bins_flanked.tsv")),
  min10 = file.path(drosophilaDataDir, paste0("Dm_UVA_10min_",rep),
                    paste0("Dm_UVA_10min_",rep,"_singlenuc_context_mutations_gene_bins_flanked.tsv")),
  min20 = file.path(drosophilaDataDir, paste0("Dm_UVA_20min_",rep),
                    paste0("Dm_UVA_20min_",rep,"_singlenuc_context_mutations_gene_bins_flanked.tsv")),
  min30 = file.path(drosophilaDataDir, paste0("Dm_UVA_30min_",rep),
                    paste0("Dm_UVA_30min_",rep,"_singlenuc_context_mutations_gene_bins_flanked.tsv"))
)
noUVA30minGeneBinFlankedFilePath = file.path(
  drosophilaDataDir, "Dm_no_UVA_30min_rep1", "Dm_no_UVA_30min_rep1_singlenuc_context_mutations_gene_bins_flanked.tsv"
)

noUVGeneBinFlankedColoredFilePath = sub(".tsv", "_colored.tsv", noUVGeneBinFlankedFilePath)
uvaGeneBinFlankedColoredFilePaths = sapply(
  uvaGeneBinFlankedFilePaths, function(x) sub(".tsv", "_colored.tsv", x)
)
noUVA30minGeneBinFlankedColoredFilePath = sub(".tsv", "_colored.tsv", noUVA30minGeneBinFlankedFilePath)


# Parse the gene bin files into counts tables.
noUVGeneBinFlanked = parseGeneBinData(noUVGeneBinFlankedFilePath)
uvaGeneBinFlanked = mapply(
  parseGeneBinData, uvaGeneBinFlankedFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE
)
noUVA30minGeneBinFlanked = parseGeneBinData(noUVA30minGeneBinFlankedFilePath, scalingFactor = noUVAScalingFactor)

noUVGeneBinFlankedColored = parseGeneBinData(noUVGeneBinFlankedColoredFilePath)
uvaGeneBinFlankedColored = mapply(
  parseGeneBinData, uvaGeneBinFlankedColoredFilePaths,
  scalingFactor = uvaScalingFactors, SIMPLIFY = FALSE
)
noUVA30minGeneBinFlankedColored = parseGeneBinData(noUVA30minGeneBinFlankedColoredFilePath, scalingFactor = noUVAScalingFactor)
```


Plot uncolored bins across all chromosomes.
```{r genome-wide_bins, fig.width = 12, fig.height=5}
options(scipen=10000)
createGgplotBinPlots(noUV10.000bp, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Feature_Counts",
                     title = "No UV", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs")
createGgplotBinPlots(uva10.000bp$min0, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Scaled_Feature_Counts",
                     title = "UVA 0min", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs (Scaled)")
createGgplotBinPlots(uva10.000bp$min10, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Scaled_Feature_Counts",
                     title = "UVA 10min", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs (Scaled)")
createGgplotBinPlots(uva10.000bp$min20, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Scaled_Feature_Counts",
                     title = "UVA 20min", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs (Scaled)")
createGgplotBinPlots(uva10.000bp$min30, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Scaled_Feature_Counts",
                     title = "UVA 30min", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs (Scaled)")
createGgplotBinPlots(noUVA30min10.000bp, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Scaled_Feature_Counts",
                     title = "No UVA 30min", ylim = c(0,5*10**5), colorPlot = FALSE,
                     yAxisLabel = "CPDs (Scaled)")
```

```{r genome-wide_bins_fraction_remaining, fig.width = 12, fig.height=5}
options(scipen=10000)

createGgplotBinPlots(uva10.000bp$min0, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Raw_To_Background_Ratio",
                     title = "UVA 0min", ylim = c(0,1), colorPlot = FALSE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min10, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Raw_To_Background_Ratio",
                     title = "UVA 10min", ylim = c(0,1), colorPlot = FALSE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min20, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Raw_To_Background_Ratio",
                     title = "UVA 20min", ylim = c(0,1), colorPlot = FALSE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min30, list(c("chr2L","chr2R"), c("chr3L","chr3R"), c("chr4"), c("chrX")),
                     "Raw_To_Background_Ratio",
                     title = "UVA 30min", ylim = c(0,1), colorPlot = FALSE,
                     yAxisLabel = "CPD Fraction Remaining")
```

Narrow in on chr3R
```{r genome-wide_bins_single_arm_colored, fig.width = 12, fig.height=5}
options(scipen=10000)
createGgplotBinPlots(noUV10.000bp, list("chr3R"), "Feature_Counts",
                     title = "No UV", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = "CPDs")
createGgplotBinPlots(uva10.000bp$min0, list("chr3R"), "Scaled_Feature_Counts",
                     title = "UVA 0min", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = expression("log"[2]*"(Repair/Damage)"))
createGgplotBinPlots(uva10.000bp$min10, list("chr3R"), "Scaled_Feature_Counts",
                     title = "UVA 10min", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = expression("log"[2]*"(Repair/Damage)"))
createGgplotBinPlots(uva10.000bp$min20, list("chr3R"), "Scaled_Feature_Counts",
                     title = "UVA 20min", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = expression("log"[2]*"(Repair/Damage)"))
createGgplotBinPlots(uva10.000bp$min30, list("chr3R"), "Scaled_Feature_Counts",
                     title = "UVA 30min", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = "CPDs (Scaled)")
createGgplotBinPlots(noUVA30min10.000bp, list("chr3R"), "Scaled_Feature_Counts",
                     title = "No UVA 30min", ylim = c(0,5*10**5), colorPlot = TRUE,
                     yAxisLabel = "CPDs (Scaled)")
```

```{r genome-wide_bins_single_arm_colored_fraction_remaining, fig.width = 12, fig.height=5}
options(scipen=10000)

createGgplotBinPlots(uva10.000bp$min0, list("chr3R"), "Raw_To_Background_Ratio",
                     title = "UVA 0min", ylim = c(0,1), colorPlot = TRUE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min10, list("chr3R"), "Raw_To_Background_Ratio",
                     title = "UVA 10min", ylim = c(0,1), colorPlot = TRUE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min20, list("chr3R"), "Raw_To_Background_Ratio",
                     title = "UVA 20min", ylim = c(0,1), colorPlot = TRUE,
                     yAxisLabel = "CPD Fraction Remaining")
createGgplotBinPlots(uva10.000bp$min30, list("chr3R"), "Raw_To_Background_Ratio",
                     title = "UVA 30min", ylim = c(0,1), colorPlot = TRUE,
                     yAxisLabel = "CPD Fraction Remaining")

```

Plot boxplots of binned CPD counts
```{r genome-wide_bins_boxplots}
plotLogRatioDistribution(noUV10.000bp, BOXPLOT, 
                         title = "No UV", "Feature_Counts",
                         yAxisLabel = "CPDs", ylim = c(0,10**5))
plotLogRatioDistribution(uva10.000bp$min0, BOXPLOT, 
                         title = "UVA 0min", "Scaled_Feature_Counts",
                         yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5))
plotLogRatioDistribution(uva10.000bp$min10, BOXPLOT, 
                         title = "UVA 10min", "Scaled_Feature_Counts",
                         yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5))
plotLogRatioDistribution(uva10.000bp$min20, BOXPLOT, 
                         title = "UVA 20min", "Scaled_Feature_Counts",
                         yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5))
plotLogRatioDistribution(uva10.000bp$min30, BOXPLOT, 
                         title = "UVA 30min", "Scaled_Feature_Counts",
                         yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**4))
plotLogRatioDistribution(noUVA30min10.000bp, BOXPLOT, 
                         title = "No UVA 30min", "Scaled_Feature_Counts",
                         yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5))
```

```{r genome-wide_bins_boxplots_fraction_remaining}
plotLogRatioDistribution(uva10.000bp$min0, BOXPLOT, 
                         title = "UVA 0min", "Raw_To_Background_Ratio",
                         yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1))
plotLogRatioDistribution(uva10.000bp$min10, BOXPLOT, 
                         title = "UVA 10min", "Raw_To_Background_Ratio",
                         yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1))
plotLogRatioDistribution(uva10.000bp$min20, BOXPLOT, 
                         title = "UVA 20min", "Raw_To_Background_Ratio",
                         yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1))
plotLogRatioDistribution(uva10.000bp$min30, BOXPLOT, 
                         title = "UVA 30min", "Raw_To_Background_Ratio",
                         yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1))
```

Boxplots of binned CPD counts stratified by genic vs. intergenic regions
```{r genic_vs_intergenic_boxplots}
plotLogRatioDistribution(noUV10.000bpGenicVsIntergenic, BOXPLOT, yData = "Feature_Counts",
                         title = "No UV Genic Vs. Intergenic", yAxisLabel = "CPDs", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min0, BOXPLOT, yData = "Scaled_Feature_Counts",
                         title = "UVA 0min Genic Vs. Intergenic", yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min10, BOXPLOT, yData = "Scaled_Feature_Counts",
                         title = "UVA 10min Genic Vs. Intergenic", yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min20, BOXPLOT, yData = "Scaled_Feature_Counts",
                         title = "UVA 20min Genic Vs. Intergenic", yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min30, BOXPLOT, yData = "Scaled_Feature_Counts",
                         title = "UVA 30min Genic Vs. Intergenic", yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(noUVA30min10.000bpGenicVsIntergenic, BOXPLOT, yData = "Scaled_Feature_Counts",
                         title = "No UVA 30min Genic Vs. Intergenic", yAxisLabel = "CPDs (Scaled)", ylim = c(0,10**5),
                         facetColumn = "Genic_Or_Intergenic")
```

```{r genic_vs_intergenic_boxplots_fraction_remaining}
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min0, BOXPLOT, yData = "Raw_To_Background_Ratio",
                         title = "UVA 0min Genic Vs. Intergenic", yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min10, BOXPLOT, yData = "Raw_To_Background_Ratio",
                         title = "UVA 10min Genic Vs. Intergenic", yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min20, BOXPLOT, yData = "Raw_To_Background_Ratio",
                         title = "UVA 20min Genic Vs. Intergenic", yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1),
                         facetColumn = "Genic_Or_Intergenic")
plotLogRatioDistribution(uva10.000bpGenicVsIntergenic$min30, BOXPLOT, yData = "Raw_To_Background_Ratio",
                         title = "UVA 30min Genic Vs. Intergenic", yAxisLabel = "CPD Fraction Remaining", ylim = c(0,1),
                         facetColumn = "Genic_Or_Intergenic")
```


Plot CPDs over time
```{r repair_over_time}
plotLogRatioMediansOverTime(uva10.000bp, timePoints = c(0, 10, 20, 30), yData = "Scaled_Feature_Counts",
                            title = "With UVA", yAxisLabel = "CPDs (Scaled)",
                            xAxisLabel = "Repair Timepoint (minutes)", ylim = c(0,10**5))
```

```{r repair_over_time_fraction_remaining}
plotLogRatioMediansOverTime(uva10.000bp, timePoints = c(0, 10, 20, 30), yData = "Raw_To_Background_Ratio",
                            title = "UVA CPD Timescale", yAxisLabel = "CPD Fraction Remaining",
                            xAxisLabel = "Repair Timepoint (minutes)", ylim = c(0,1))
```

Whole genome TS vs. NTS Plots
```{r TS_to_NTS_repair}
plotGeneBinData(noUVGeneBinFlanked, title = "Gene Fractions No UV",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlanked$min0, title = "Gene Fractions UVA 0min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlanked$min10, title = "Gene Fractions UVA 10min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlanked$min20, title = "Gene Fractions UVA 20min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlanked$min30, title = "Gene Fractions UVA 30min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(noUVA30minGeneBinFlanked, title = "Gene Fractions No UVA 30min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
```


Colored TS Vs. NTS Plots
```{r TS_to_NTS_repair_by_domain}
plotGeneBinData(noUVGeneBinFlankedColored, title = "Gene Fractions No UV",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlankedColored$min0, title = "Gene Fractions UVA 0min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlankedColored$min10, title = "Gene Fractions UVA 10min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlankedColored$min20, title = "Gene Fractions UVA 20min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(uvaGeneBinFlankedColored$min30, title = "Gene Fractions UVA 30min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
plotGeneBinData(noUVA30minGeneBinFlankedColored, title = "Gene Fractions No UVA 30min",
                yAxisLabel = expression("log"[2]*"(TS/NTS CPDs)"), ylim = c(-1,1))
```


#Periodicity Analysis

Get the relevant data files for the NRL analysis
```{r prep_nucleosome_map_periodicity_data}
source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))

# Get nucleosome self counts
nucSelfCountsFilePaths = list(all = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                              black = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_BLACK_domain_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                              blue = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_BLUE_domain_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                              green = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_GREEN_domain_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                              red = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_RED_domain_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                              yellow = file.path(drosophilaDataDir, "nucleosomes",
                                "S2_nucleosome_map_YELLOW_domain_nuc-group_self_raw_nucleosome_mutation_counts.tsv"))

# Get nucleosome subset self counts
nucSelfCountsSubsetFilePaths = list(black = file.path(drosophilaDataDir, "nucleosomes",
                        "S2_nucleosome_map_BLACK_domain_subset_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                      blue = file.path(drosophilaDataDir, "nucleosomes",
                        "S2_nucleosome_map_BLUE_domain_subset_nuc-group_self_raw_nucleosome_mutation_counts.tsv"),
                      yellow = file.path(drosophilaDataDir, "nucleosomes",
                        "S2_nucleosome_map_YELLOW_domain_subset_nuc-group_self_raw_nucleosome_mutation_counts.tsv"))

yellowGenicNucSelfCounts = fread(file.path(drosophilaDataDir, "nucleosomes",
                                           "S2_nucleosome_map_YELLOW_domain_genic_nuc-group_self_counts.tsv"))
yellowIntergenicNucSelfCounts = fread(file.path(drosophilaDataDir, "nucleosomes",
                                        "S2_nucleosome_map_YELLOW_domain_intergenic_nuc-group_self_counts.tsv"))

# Convert self counts to lomb-scargle periodograms.
nucSelfCounts = lapply(nucSelfCountsFilePaths, fread)
nucSelfCountsLombResult = lapply(nucSelfCounts, function(x){getLombResult(x, TRANSLATIONAL, 147)})
nucSelfCountsPeriodAndSNR = lapply(nucSelfCountsLombResult, getPeakPeriodicityAndSNR)
nucSelfCountsLombResult = rbindlist(lapply(seq_along(nucSelfCountsLombResult), 
                                    function(i){data.table(Color_Domain = names(nucSelfCountsLombResult)[i], 
                                                           Periods = nucSelfCountsLombResult[[i]]$scanned,
                                                           Power = nucSelfCountsLombResult[[i]]$power)}))

nucSelfCountsSubset = lapply(nucSelfCountsSubsetFilePaths, fread)
nucSelfCountsSubsetLombResult = lapply(nucSelfCountsSubset, function(x){getLombResult(x, TRANSLATIONAL, 147)})
nucSelfCountsSubsetLombResult = rbindlist(lapply(seq_along(nucSelfCountsSubsetLombResult), 
                                    function(i){data.table(Color_Domain = names(nucSelfCountsSubsetLombResult)[i], 
                                                           Periods = nucSelfCountsSubsetLombResult[[i]]$scanned,
                                                           Power = nucSelfCountsSubsetLombResult[[i]]$power)}))

# Make two more sets of lomb results, one for inner data and one for outer.
nucSelfCountsOutsideLR = lapply(nucSelfCounts, function(x){getLombResult(x, TRANSLATIONAL, 500)})
nucSelfCountsOutsideLR = rbindlist(lapply(seq_along(nucSelfCountsOutsideLR), 
                                    function(i){data.table(Color_Domain = names(nucSelfCountsOutsideLR)[i], 
                                                           Periods = nucSelfCountsOutsideLR[[i]]$scanned,
                                                           Power = nucSelfCountsOutsideLR[[i]]$power)}))

nucSelfCountsInsideLR = lapply(nucSelfCounts, 
                               function(x){getLombResult(x[Dyad_Position >= -500 & Dyad_Position <= 500], 
                                                         TRANSLATIONAL, 147)})
nucSelfCountsInsideLR = rbindlist(lapply(seq_along(nucSelfCountsInsideLR), 
                                    function(i){data.table(Color_Domain = names(nucSelfCountsInsideLR)[i], 
                                                           Periods = nucSelfCountsInsideLR[[i]]$scanned,
                                                           Power = nucSelfCountsInsideLR[[i]]$power)}))

yellowGenicLombResult = getLombResult(yellowGenicNucSelfCounts, TRANSLATIONAL, 147)
yellowIntergenicLombResult = getLombResult(yellowIntergenicNucSelfCounts, TRANSLATIONAL, 147)

yellowGenicVIntergenicLombResult = rbindlist(list(data.table(Color_Domain = "gold2", Line_Type = "solid",
                                                             Periods = yellowGenicLombResult$scanned,
                                                             Power = yellowGenicLombResult$power),
                                                  data.table(Color_Domain = "darkorange", Line_Type = "dashed",
                                                             Periods = yellowIntergenicLombResult$scanned, 
                                                             Power = yellowIntergenicLombResult$power)))
```


Plot lomb results for the NRL analysis
```{r nucleosome_map_periodograms}
plotLombResult(nucSelfCountsLombResult[Color_Domain == "all", .(Periods, Power)], 
               title = "NRL Periodogram (All Nucleosomes)")
plotLombResult(nucSelfCountsLombResult[Color_Domain != "all"], 
               title = "NRL Periodogram (Color Domains)")
plotLombResult(rbindlist(list(nucSelfCountsSubsetLombResult, 
                              nucSelfCountsLombResult[Color_Domain == "green" | Color_Domain == "red"])), 
               title = "NRL Periodogram (Subset)")
```


```{r setup-chunk2}
mutperiodData = file.path(drosophilaDataDir, paste0("Marian_Drosophila_CPD-seq_",rep,"_periodicity_analysis.rda"))
knitr::opts_template$set(mutperiodData = list(cache = TRUE, 
                                              cache.extra = na.fail(tools::md5sum(mutperiodData))))
```

Get the relevant data files for the analysis of the XR-seq data.
```{r prep_periodicity_data, opts.label = "mutperiodData"}
# Organize the big ol' mutperiod data object.
load(mutperiodData)
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

noUVTrans = list(
  all = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_nuc-group_raw")]],
  black = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_BLACK_domain_nuc-group_raw")]],
  blue = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_BLUE_domain_nuc-group_raw")]],
  green = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_GREEN_domain_nuc-group_raw")]],
  red = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_RED_domain_nuc-group_raw")]],
  yellow = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_no_UV_",rep,"_YELLOW_domain_nuc-group_raw")]]
)

uvaTrans = mapply(function (x,y) list(
  all = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_nuc-group_raw")]],
  black = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_BLACK_domain_nuc-group_raw")]],
  blue = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_BLUE_domain_nuc-group_raw")]],
  green = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_GREEN_domain_nuc-group_raw")]],
  red = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_RED_domain_nuc-group_raw")]],
  yellow = mutperiodData$rawNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_YELLOW_domain_nuc-group_raw")]]
), list(min0=NULL,min10=NULL,min20=NULL,min30=NULL), list("0min","10min","20min","30min"), SIMPLIFY = FALSE)

uvaTransNormalized = mapply(function (x,y) list(
  all = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_custom_context_nuc-group_normalized")]],
  black = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_BLACK_domain_custom_context_nuc-group_normalized")]],
  blue = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_BLUE_domain_custom_context_nuc-group_normalized")]],
  green = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_GREEN_domain_custom_context_nuc-group_normalized")]],
  red = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_RED_domain_custom_context_nuc-group_normalized")]],
  yellow = mutperiodData$normalizedNucleosomeCountsTables[[paste0("Dm_UVA_",y,"_",rep,"_YELLOW_domain_custom_context_nuc-group_normalized")]]
), list(min0=NULL,min10=NULL,min20=NULL,min30=NULL), list("0min","10min","20min","30min"), SIMPLIFY = FALSE)

noUVA30minTrans = list(
  all = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_nuc-group_raw"]],
  black = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_BLACK_domain_nuc-group_raw"]],
  blue = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_BLUE_domain_nuc-group_raw"]],
  green = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_GREEN_domain_nuc-group_raw"]],
  red = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_RED_domain_nuc-group_raw"]],
  yellow = mutperiodData$rawNucleosomeCountsTables[["Dm_no_UVA_30min_rep1_YELLOW_domain_nuc-group_raw"]]
)

# Convert counts to lomb-scargle periodograms.
noUVTransLombResults = lapply(noUVTrans, function(x){getLombResult(x, TRANSLATIONAL)})
noUVTransLombResults = rbindlist(lapply(seq_along(noUVTransLombResults), 
                                  function(i){data.table(Color_Domain = names(noUVTransLombResults)[i], 
                                                         Periods = noUVTransLombResults[[i]]$scanned,
                                                         Power = noUVTransLombResults[[i]]$power)}))

uvaTransLombResults = lapply(uvaTrans, function(x){
  lapply(x, function(y) getLombResult(y, TRANSLATIONAL))
})
uvaTransLombResults = lapply(uvaTransLombResults, function(x) {
  rbindlist(lapply(seq_along(x), function(i){
    data.table(Color_Domain = names(x)[i], 
               Periods = x[[i]]$scanned,
               Power = x[[i]]$power)
  }))
})

uvaTransNormalizedLombResults = lapply(uvaTransNormalized, function(x){
  lapply(x, function(y) getLombResult(y, TRANSLATIONAL, countsColumnName = "Alternative_Normalized_Both_Strands"))
})
uvaTransNormalizedLombResults = lapply(uvaTransNormalizedLombResults, function(x) {
  rbindlist(lapply(seq_along(x), function(i){
    data.table(Color_Domain = names(x)[i], 
               Periods = x[[i]]$scanned,
               Power = x[[i]]$power)
  }))
})

noUVA30minTransLombResults = lapply(noUVA30minTrans, function(x){getLombResult(x, TRANSLATIONAL)})
noUVA30minTransLombResults = rbindlist(lapply(seq_along(noUVA30minTransLombResults), 
                                  function(i){data.table(Color_Domain = names(noUVA30minTransLombResults)[i], 
                                                         Periods = noUVA30minTransLombResults[[i]]$scanned,
                                                         Power = noUVA30minTransLombResults[[i]]$power)}))


noUVRotLombResults = lapply(noUVTrans, function(x){getLombResult(x, ROTATIONAL)})
noUVRotLombResults = rbindlist(lapply(seq_along(noUVRotLombResults), 
                                  function(i){data.table(Color_Domain = names(noUVRotLombResults)[i], 
                                                         Periods = noUVRotLombResults[[i]]$scanned,
                                                         Power = noUVRotLombResults[[i]]$power)}))

uvaRotLombResults = lapply(uvaTrans, function(x){
  lapply(x, function(y) getLombResult(y, ROTATIONAL))
})
uvaRotLombResults = lapply(uvaRotLombResults, function(x) {
  rbindlist(lapply(seq_along(x), function(i){
    data.table(Color_Domain = names(x)[i], 
               Periods = x[[i]]$scanned,
               Power = x[[i]]$power)
  }))
})

uvaRotNormalizedLombResults = lapply(uvaTransNormalized, function(x){
  lapply(x, function(y) getLombResult(y, ROTATIONAL, countsColumnName = "Alternative_Normalized_Both_Strands"))
})
uvaRotNormalizedLombResults = lapply(uvaRotNormalizedLombResults, function(x) {
  rbindlist(lapply(seq_along(x), function(i){
    data.table(Color_Domain = names(x)[i], 
               Periods = x[[i]]$scanned,
               Power = x[[i]]$power)
  }))
})

noUVA30minRotLombResults = lapply(noUVA30minTrans, function(x){getLombResult(x, ROTATIONAL)})
noUVA30minRotLombResults = rbindlist(lapply(seq_along(noUVA30minRotLombResults), 
                                  function(i){data.table(Color_Domain = names(noUVA30minRotLombResults)[i], 
                                                         Periods = noUVA30minRotLombResults[[i]]$scanned,
                                                         Power = noUVA30minRotLombResults[[i]]$power)}))


# Compile bulk data for gg facet plot
isTranslationalDataSets = grepl("nuc-group", dataSetNames, fixed = TRUE)
isUVADataSet = grepl("Dm_UVA", dataSetNames)
isSpecifiedRep = grepl(rep, dataSetNames)
isNormalized = grepl("normalized", dataSetNames)

# Gets all data for uva data sets with timepoint and domain columns.
bulkTransUVA = rbindlist(lapply(dataSetNames[isTranslationalDataSets & isUVADataSet & isSpecifiedRep & !isNormalized],
                                addTimepointAndDomainInfo, 
                                smoothCols = list("Both_Strands_Counts"),
                                expectedTimepoints = c("0min", "10min", "20min", "30min")))
bulkTransUVA[Timepoint == "0min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min0]
bulkTransUVA[Timepoint == "0min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min0]
bulkTransUVA[Timepoint == "10min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min10]
bulkTransUVA[Timepoint == "10min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min10]
bulkTransUVA[Timepoint == "20min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min20]
bulkTransUVA[Timepoint == "20min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min20]
bulkTransUVA[Timepoint == "30min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min30]
bulkTransUVA[Timepoint == "30min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min30]

for (timepoint in unique(bulkTransUVA$Timepoint)) {
  for (domain in unique(bulkTransUVA$Domain)) {
    bulkTransUVA[Timepoint == timepoint & Domain == domain,
                 Both_Strands_Normalized := Both_Strands_Counts/mean(Both_Strands_Counts)]
    bulkTransUVA[Timepoint == timepoint & Domain == domain,
                 Aligned_Strands_Normalized := Aligned_Strands_Counts/mean(Aligned_Strands_Counts)]
  }
}

bulkTransUVANormalized = rbindlist(lapply(dataSetNames[isTranslationalDataSets & isUVADataSet & isSpecifiedRep & isNormalized],
                                          addTimepointAndDomainInfo, 
                                          smoothCols = list("Alternative_Normalized_Both_Strands"),
                                          expectedTimepoints = c("0min", "10min", "20min", "30min")))


# Gets all data for rotational repair data sets with timepoint and domain columns.
bulkRotUVA = rbindlist(lapply(dataSetNames[!isTranslationalDataSets & isUVADataSet & isSpecifiedRep & !isNormalized],
                              addTimepointAndDomainInfo,
                              expectedTimepoints = c("0min", "10min", "20min", "30min")))
bulkRotUVA[Timepoint == "0min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min0]
bulkRotUVA[Timepoint == "0min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min0]
bulkRotUVA[Timepoint == "10min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min10]
bulkRotUVA[Timepoint == "10min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min10]
bulkRotUVA[Timepoint == "20min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min20]
bulkRotUVA[Timepoint == "20min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min20]
bulkRotUVA[Timepoint == "30min", Both_Strands_Scaled := Both_Strands_Counts*uvaScalingFactors$min30]
bulkRotUVA[Timepoint == "30min", Aligned_Strands_Scaled := Aligned_Strands_Counts*uvaScalingFactors$min30]

for (timepoint in unique(bulkRotUVA$Timepoint)) {
  for (domain in unique(bulkRotUVA$Domain)) {
    bulkRotUVA[Timepoint == timepoint & Domain == domain,
                 Both_Strands_Normalized := Both_Strands_Counts/mean(Both_Strands_Counts)]
    bulkRotUVA[Timepoint == timepoint & Domain == domain,
                 Aligned_Strands_Normalized := Aligned_Strands_Counts/mean(Aligned_Strands_Counts)]
  }
}

bulkRotUVANormalized = rbindlist(lapply(dataSetNames[!isTranslationalDataSets & isUVADataSet & isSpecifiedRep & isNormalized],
                                        addTimepointAndDomainInfo,
                                        expectedTimepoints = c("0min", "10min", "20min", "30min")))
```


Plot Lomb-Scargle periodograms.
```{r Lomb-Scargle_rotational_periodograms, opts.label = "mutperiodData", fig.width = 7, fig.height = 5}
# All domains combined
plotLombResult(noUVRotLombResults[Color_Domain == "all", .(Periods, Power)], 
               title = "No UV Periodogram (All Nucleosomes)")
plotLombResult(uvaRotLombResults$min0[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 0min (All Nucleosomes)")
plotLombResult(uvaRotLombResults$min10[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 10min (All Nucleosomes)")
plotLombResult(uvaRotLombResults$min20[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 20min (All Nucleosomes)")
plotLombResult(uvaRotLombResults$min30[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 30min (All Nucleosomes)")
plotLombResult(noUVA30minRotLombResults[Color_Domain == "all", .(Periods, Power)], 
               title = "No UVA 30min (All Nucleosomes)")

# Individual domains plotted together
plotLombResult(noUVRotLombResults[Color_Domain != "all"], 
               title = "No UV Periodogram (Color Domains)")
plotLombResult(uvaRotLombResults$min0[Color_Domain != "all"], 
               title = "UVA 0min (Color Domains)")
plotLombResult(uvaRotLombResults$min10[Color_Domain != "all"], 
               title = "UVA 10min (Color Domains)")
plotLombResult(uvaRotLombResults$min20[Color_Domain != "all"], 
               title = "UVA 20min (Color Domains)")
plotLombResult(uvaRotLombResults$min30[Color_Domain != "all"], 
               title = "UVA 30min (Color Domains)")
plotLombResult(noUVA30minRotLombResults[Color_Domain != "all"], 
               title = "No UVA 30min (Color Domains)")
```

```{r Lomb-Scargle_rotational_periodograms_fraction_remaining, opts.label = "mutperiodData", fig.width = 7, fig.height = 5}
# All domains combined
plotLombResult(uvaRotNormalizedLombResults$min0[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 0min CPD fraction (All Nucleosomes)")
plotLombResult(uvaRotNormalizedLombResults$min10[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 10min CPD fraction (All Nucleosomes)")
plotLombResult(uvaRotNormalizedLombResults$min20[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 20min CPD fraction (All Nucleosomes)")
plotLombResult(uvaRotNormalizedLombResults$min30[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 30min CPD fraction (All Nucleosomes)")

# Individual domains plotted together
plotLombResult(uvaRotNormalizedLombResults$min0[Color_Domain != "all"], 
               title = "UVA 0min CPD fraction (Color Domains)")
plotLombResult(uvaRotNormalizedLombResults$min10[Color_Domain != "all"], 
               title = "UVA 10min CPD fraction (Color Domains)")
plotLombResult(uvaRotNormalizedLombResults$min20[Color_Domain != "all"], 
               title = "UVA 20min CPD fraction (Color Domains)")
plotLombResult(uvaRotNormalizedLombResults$min30[Color_Domain != "all"], 
               title = "UVA 30min CPD fraction (Color Domains)")
```


```{r Lomb-Scargle_translational_periodograms, opts.label = "mutperiodData", fig.width = 7, fig.height = 5}
# All domains combined
plotLombResult(noUVTransLombResults[Color_Domain == "all", .(Periods, Power)], 
               title = "No UV Periodogram (All Nucleosomes)")
plotLombResult(uvaTransLombResults$min0[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 0min (All Nucleosomes)")
plotLombResult(uvaTransLombResults$min10[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 10min (All Nucleosomes)")
plotLombResult(uvaTransLombResults$min20[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 20min (All Nucleosomes)")
plotLombResult(uvaTransLombResults$min30[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 30min (All Nucleosomes)")
plotLombResult(noUVA30minTransLombResults[Color_Domain == "all", .(Periods, Power)], 
               title = "No UVA 30min (All Nucleosomes)")

# Individual domains plotted together
plotLombResult(noUVTransLombResults[Color_Domain != "all"], 
               title = "No UV Periodogram (Color Domains)")
plotLombResult(uvaTransLombResults$min0[Color_Domain != "all"], 
               title = "UVA 0min (Color Domains)")
plotLombResult(uvaTransLombResults$min10[Color_Domain != "all"], 
               title = "UVA 10min (Color Domains)")
plotLombResult(uvaTransLombResults$min20[Color_Domain != "all"], 
               title = "UVA 20min (Color Domains)")
plotLombResult(uvaTransLombResults$min30[Color_Domain != "all"], 
               title = "UVA 30min (Color Domains)")
plotLombResult(noUVA30minTransLombResults[Color_Domain != "all"], 
               title = "No UVA 30min (Color Domains)")
```

```{r Lomb-Scargle_translational_periodograms_fraction_remaining, opts.label = "mutperiodData", fig.width = 7, fig.height = 5}
# All domains combined
plotLombResult(uvaTransNormalizedLombResults$min0[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 0min CPD fraction (All Nucleosomes)")
plotLombResult(uvaTransNormalizedLombResults$min10[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 10min CPD fraction (All Nucleosomes)")
plotLombResult(uvaTransNormalizedLombResults$min20[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 20min CPD fraction (All Nucleosomes)")
plotLombResult(uvaTransNormalizedLombResults$min30[Color_Domain == "all", .(Periods, Power)], 
               title = "UVA 30min CPD fraction (All Nucleosomes)")

# Individual domains plotted together
plotLombResult(uvaTransNormalizedLombResults$min0[Color_Domain != "all"], 
               title = "UVA 0min CPD fraction (Color Domains)")
plotLombResult(uvaTransNormalizedLombResults$min10[Color_Domain != "all"], 
               title = "UVA 10min CPD fraction (Color Domains)")
plotLombResult(uvaTransNormalizedLombResults$min20[Color_Domain != "all"], 
               title = "UVA 20min CPD fraction (Color Domains)")
plotLombResult(uvaTransNormalizedLombResults$min30[Color_Domain != "all"], 
               title = "UVA 30min CPD fraction (Color Domains)")
```


Genome-wide rotational nucleosome patterns
```{r Genome-wide_rotational_periodicities, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_0min_",rep,"_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min0),
                title = "UVA 0min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_10min_",rep,"_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min10),
                title = "UVA 10min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_20min_",rep,"_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min20),
                title = "UVA 20min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_30min_",rep,"_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min30),
                title = "UVA 30min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA 30min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
```

```{r Genome-wide_rotational_periodicities_fraction_remaining, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_0min_",rep,"_custom_context_30linker+_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 0min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_10min_",rep,"_custom_context_30linker+_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 10min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_20min_",rep,"_custom_context_30linker+_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 20min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_30min_",rep,"_custom_context_30linker+_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 30min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
```

Color domain rotational patterns
```{r No_UV_color_domain_rotational_periodicities, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_BLACK_domain_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV BLACK", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_BLUE_domain_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV BLUE", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_GREEN_domain_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV GREEN", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_RED_domain_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV RED", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_YELLOW_domain_30linker+_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV YELLOW", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
```


```{r UVA_color_domain_rotational_periodicities, fig.width = 12, fig.height = 5, opts.label = "mutperiodData"}
plotBulkCountsData(bulkRotUVA, dataCol = "Both_Strands_Normalized", yAxisLabel = "Relative Damage",
                   expectedTimepoints = c("0min", "10min", "20min", "30min"))
```

```{r UVA_color_domain_rotational_periodicities_fraction_remaining, fig.width = 12, fig.height = 5, opts.label = "mutperiodData"}
plotBulkCountsData(bulkRotUVANormalized, dataCol = "Alternative_Normalized_Both_Strands", yAxisLabel = "CPD Fraction Remaining",
                   ylim = c(-0.1,1.1), expectedTimepoints = c("0min", "10min", "20min", "30min"))
```


```{r No_UVA_color_domain_rotational_periodicities, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_BLACK_domain_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA BLACK", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_BLUE_domain_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA BLUE", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_GREEN_domain_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA GREEN", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_RED_domain_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA RED", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_YELLOW_domain_30linker+_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA YELLOW", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
```

Genome-wide translational nucleosome patterns
```{r repair_and_damage_translational_data, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_0min_",rep,"_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min0),
                title = "UVA 0min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_10min_",rep,"_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min10),
                title = "UVA 10min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_20min_",rep,"_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min20),
                title = "UVA 20min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_30min_",rep,"_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts", scalingFactor = uvaScalingFactors$min30),
                title = "UVA 30min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA 30min", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
```

```{r repair_and_damage_translational_data_fraction_remaining, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_0min_",rep,"_custom_context_nuc-group_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 0min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_10min_",rep,"_custom_context_nuc-group_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 10min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_20min_",rep,"_custom_context_nuc-group_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 20min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_UVA_30min_",rep,"_custom_context_nuc-group_normalized")]],
                                     dataCol = "Alternative_Normalized_Both_Strands"),
                title = "UVA 30min", ylim = c(0,1), yAxisLabel = "CPD Fraction Remaining", dataCol = "Alternative_Normalized_Both_Strands")
```


Color domain translational patterns
```{r No_UV_color_domain_translational_periodicities, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_BLACK_domain_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV BLACK", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_BLUE_domain_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV BLUE", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_GREEN_domain_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV GREEN", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_RED_domain_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV RED", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames[[paste0("Dm_no_UV_",rep,"_YELLOW_domain_nuc-group_raw")]],
                                     dataCol = "Both_Strands_Counts"),
                title = "No UV YELLOW", ylim = NULL, yAxisLabel = "CPDs", dataCol = "Both_Strands_Counts")
```


```{r UVA_color_domain_translational_periodicities, fig.width = 12, fig.height = 5, opts.label = "mutperiodData"}
plotBulkCountsData(bulkTransUVA, dataCol = "Both_Strands_Normalized", yAxisLabel = "Relative Damage",
                   expectedTimepoints = c("0min", "10min", "20min", "30min"))
```

```{r UVA_color_domain_translational_periodicities_fraction_remaining, fig.width = 12, fig.height = 5, opts.label = "mutperiodData"}
plotBulkCountsData(bulkTransUVANormalized, dataCol = "Alternative_Normalized_Both_Strands", yAxisLabel = "Relative Damage",
                   ylim = c(-0.1,1.1), expectedTimepoints = c("0min", "10min", "20min", "30min"))
```


```{r No_UVA_color_domain_translational_periodicities, opts.label = "mutperiodData", fig.width = 9, fig.height = 5}
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_BLACK_domain_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA BLACK", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_BLUE_domain_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA BLUE", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_GREEN_domain_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA GREEN", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_RED_domain_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA RED", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
plotPeriodicity(parsePeriodicityData(dataSetNames$`Dm_no_UVA_30min_rep1_YELLOW_domain_nuc-group_raw`,
                                     dataCol = "Both_Strands_Counts", scalingFactor = noUVAScalingFactor),
                title = "No UVA YELLOW", ylim = NULL, yAxisLabel = "CPDs (Scaled)", dataCol = "Both_Strands_Counts")
```
